HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-17 hermes_paper/hermes_paper.tex
small correction

The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}. Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarcks. This results is partially induce by the use of TBATS per-time-series predictors which achieves striking result also on the test set. Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}. With the second application, two importants conclusion can be done. Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks. Secondly, the accuracy gap between the 2 hybrid candidate validate the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.

>>>>

The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}. Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarcks. This results is partially induced by the use of TBATS per-time-series predictors which achieves striking results on the test set. Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}. With this second application, two importants conclusion can be done. Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks. Secondly, the accuracy gap between the 2 hybrid candidates validate the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.
